### 2017-11-16 linearity-2018/introduction.tex
One paragraph away from the full introductino.

Our main contributions in this paper are to the Lambek Calculus, but
we make use of a new more general framework that will put this work in
line with planned future work.  Suppose $\cat{M}_1$ and $\cat{M}_2$
are two categories with a bifunctor $\odot_i : \cat{M}_i \times
\cat{M}_i \mto \cat{M}_i$, a distinguished object $I_i \in
\mathsf{Obj}(\cat{M}_i)$, and the two natural isomorphisms $\lambda_A
: A \odot I_i \mto A$ and $\rho_A : I_i \odot A \mto A$.  We call
these categories \emph{magmoidal categories with a unit}.  Examples of
magmoidal categories with a unit are monoidal categories, symmetric
monoidal categories, and cartesian closed categories.  Benton's LNL
models can be generalized to magmodial categories.  Simply, take an
adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called an
\emph{adjoint model} where the functors $F$ and $G$ preserve the
magmoidal structure similarly to monoidal functors, but without the
coherence diagram for the associator.  Now if we add to $\cat{M}_1$
and $\cat{M}_2$ some structural rules, for example, by making
$\cat{M}_1$ a symmetric monoidal category and $\cat{M}_2$ a monoidal
category, then we obtain an adjoint model that corresponds to a logic
where intuitionistic linear logic ($\cat{M}_1$) and the Lambek
calculus ($\cat{M}_2$) are mixed similarly to LNL models.  However,
this also leads to a new solution to an existing problem.

Linguists have wondered if a modality for exchange can be added to the
Lambek Calculus similarly to how the of-course! modality adds
weakening and contraction to linear logic.  de Paiva and
Eades~\cite{?} show that this is possible by adding a modality $\kappa
A$ with the property that $(\kappa A \otimes B) \multimap (B \otimes
\kappa A)$.  The adjoint model introduced above induces the modality
$eA = F(G\,A)$ with the property $eA \otimes eB \multimap eB \otimes
eA$.  Thus providing a second solution to the problem, but we go
further, and show such a modality can be given for associativity. It
arises as the induced comonad of the adjoint model where $\cat{M}_1$
is a monoidal category, and $\cat{M}_2$ is a magmoidal category with a
unit.

>>>>

Our main contributions in this paper are to the Lambek Calculus, but
we make use of a new more general framework that will put this work in
line with planned future work.  Suppose $\cat{M}_1$ and $\cat{M}_2$
are two categories with a bifunctor $\odot_i : \cat{M}_i \times
\cat{M}_i \mto \cat{M}_i$, a distinguished object $I_i \in
\mathsf{Obj}(\cat{M}_i)$, and the two natural isomorphisms $\lambda_A
: A \odot I_i \mto A$ and $\rho_A : I_i \odot A \mto A$.  We call
these categories \emph{magmoidal categories with a unit}.  Examples of
magmoidal categories with a unit are monoidal categories, symmetric
monoidal categories, and cartesian closed categories.

Benton's LNL models can be generalized to magmodial categories.
Simply, take an adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called
an \emph{adjoint model} where the functors $F$ and $G$ preserve the
magmoidal structure similarly to monoidal functors, but without the
coherence diagram for the associator.  Now if we add to $\cat{M}_1$
and $\cat{M}_2$ some structural rules, for example, by making
$\cat{M}_1$ a symmetric monoidal category and $\cat{M}_2$ a monoidal
category, then we obtain an adjoint model that corresponds to a logic
where intuitionistic linear logic ($\cat{M}_1$) and the Lambek
calculus ($\cat{M}_2$) are mixed similarly to LNL models.  However,
this also leads to a new solution to an existing problem.

Linguists have wondered if a modality for exchange can be added to the
Lambek Calculus similarly to how the of-course! modality adds
weakening and contraction to linear logic.  de Paiva and
Eades~\cite{?} show that this is possible by adding a modality $\kappa
A$ with the property that $(\kappa A \otimes B) \multimap (B \otimes
\kappa A)$.  The adjoint model introduced above induces the modality
$eA = F(G\,A)$ with the property $eA \otimes eB \multimap eB \otimes
eA$.  Thus providing a second solution to the problem, but we go
further, and show such a modality can be given for associativity. It
arises as the induced comonad of the adjoint model where $\cat{M}_1$
is a monoidal category, and $\cat{M}_2$ is a vanilla magmoidal
category with a unit.  Then we will obtain the property $(aA \otimes
aB) \otimes aC) \multimap aA \otimes (aB \otimes aC)$.

Linguists as well as computer scientists have found many applications
of substructural logics that contain more than one tensor product
satisfying different structural rules.  For example, a commutative
tensor product and a non-commutative tensor product within the same
logic.  An example of such a logic is the logic of bunched
implications, but there sequents $\Gamma \vdash A$ depend on contexts
$\Gamma$ that are trees with multiple different branching nodes
instead of lists.  The branching nodes are necessary to accommodate
multiple different tensor products with different structural
properties.  We show how adjoint models can be used to build similar
logics, but without the need for multiple different branching nodes.
Furthermore, adjoints compose, and this property can be exploited to
compose modalities.
